### 2022-03-24 draft.tex
Deploying to gh-pages from @ emuise/ms-assessingRepresentation@0f2e686ab9eceeb16cc775de6c7e3b66c21226bc 🚀

The province of British Columbia, Canada, covers 94.4 million ha, of
which approximately 64\% is forested (BC Ministry of Forests 2003), and
encapsulates a wide variety of biomes and ecosystems. This diversity of
ecosystems is in part due to the large area as well as variations in
topography and climate. The existing Biogeoclimatic Ecosystem
Classification (BEC) system disaggregates BC ecosystems into zones
(Pojar et al. 1987). The broadest classification delineates 16 zones,
which are further broken down into subzones, variants, and phases based
on microclimate, precipitation, and topography (Pojar et al. 1987,
Meidinger and Pojar 1991). As a result, BEC zones vary widely in size
(ranging from 0.25 million ha to 17.5 million ha), and in number of
subzones (from 1 to 43; see \{tbl.~\ref{tbl:bec-table}\}).

@@

Forest structural attributes vary between PA and UA in BC
(fig.~\ref{fig:structure-3d-scatter}). The largest differences between
PA and UA are found in canopy structure in the Coastal Douglas-fir BEC
zone, with the protected area having much higher canopy structure
values. As shown in fig.~\ref{fig:t-test-plot}, forests are commonly
significantly different when comparing PA vs UA across all attributes.
When examining the forests on an BEC zone level, only one BEC zone has a
\textgreater5\% difference in vertical forest structure (co-efficient of
variation in vegetation returns), six BEC zones have \textgreater5\%
difference in canopy cover, and five BEC zones have a \textgreater5\%
difference in canopy height. Ponderosa pine has large differences in
canopy cover and canopy height (\textgreater5\%), but minor differences
in elevation covariance (only 0.25\%; \{tbl.~\ref{tbl:vectab}\}). PA in
the Ponderosa Pine, Interior Mountain Heather Alpine, and Coastal
Douglas-fir have more aboveground biomass than in UA in corresponding
areas (fig.~\ref{fig:structure-3d-scatter}).

@@

In high elevation ecosystems, Boreal Altai Fescue Alpine dominates the
PA proportions above 3000m, replacing the Coastal Mountain-Heather
Alpine ecosystem found in UA (fig.~\ref{fig:bec-elev}). These zones were
both protected at rates above the average (fig.~\ref{fig:bec-conch}),
and above the Aichi biodiversity targets. Interior mountain-heather
alpine had large differences in canopy cover and canopy height, while
Boreal Altai Fescue Alpine only showed large differences in height. The
Coastal Mountain-heather Alpine did not any have large forest structural
attribute differences (\{tbl.~\ref{tbl:vectab}\}).

@@

Utilizing this information on the proportion of BEC zones protected
(fig.~\ref{fig:bec-conch}), as well as their forest structural
attributes (\{tbl.~\ref{tbl:vectab}\}), it is possible to identify which
forest structures need to be added to the PA network in BC. Those BEC
zones with large differences (identified as being \textgreater5\% change
from PA to UA) suggest additional protection is needed to encapsulate
these underrepresented forest structures. For example: the forests in
the Bunchgrass zone have large differences in both canopy cover and
canopy height, with the PA having larger values in both attributes
(\{tbl.~\ref{tbl:vectab}\}). New PA in this BEC zone should contain
forests with shorter and more open forests. A future avenue of research
could be to incorporate forest structural attributes into spatially
optimized PA placement approaches (Christensen et al. 2009).

>>>>

The province of British Columbia, Canada, covers 94.4 million ha, of
which approximately 64\% is forested (BC Ministry of Forests 2003), and
encapsulates a wide variety of biomes and ecosystems. This diversity of
ecosystems is in part due to the large area as well as variations in
topography and climate. The existing Biogeoclimatic Ecosystem
Classification (BEC) system disaggregates BC ecosystems into zones
(Pojar et al. 1987). The broadest classification delineates 16 zones,
which are further broken down into subzones, variants, and phases based
on microclimate, precipitation, and topography (Pojar et al. 1987,
Meidinger and Pojar 1991). As a result, BEC zones vary widely in size
(ranging from 0.25 million ha to 17.5 million ha), and in number of
subzones (from 1 to 43; see tbl.~\ref{tbl:bec-table}).

@@

Forest structural attributes vary between PA and UA in BC
(fig.~\ref{fig:structure-3d-scatter}). The largest differences between
PA and UA are found in canopy structure in the Coastal Douglas-fir BEC
zone, with the protected area having much higher canopy structure
values. As shown in fig.~\ref{fig:t-test-plot}, forests are commonly
significantly different when comparing PA vs UA across all attributes.
When examining the forests on an BEC zone level, only one BEC zone has a
\textgreater5\% difference in vertical forest structure (co-efficient of
variation in vegetation returns), six BEC zones have \textgreater5\%
difference in canopy cover, and five BEC zones have a \textgreater5\%
difference in canopy height. Ponderosa pine has large differences in
canopy cover and canopy height (\textgreater5\%), but minor differences
in elevation covariance (only 0.25\%; tbl.~\ref{tbl:vectab}). PA in the
Ponderosa Pine, Interior Mountain Heather Alpine, and Coastal
Douglas-fir have more aboveground biomass than in UA in corresponding
areas (fig.~\ref{fig:structure-3d-scatter}).

@@

In high elevation ecosystems, Boreal Altai Fescue Alpine dominates the
PA proportions above 3000m, replacing the Coastal Mountain-Heather
Alpine ecosystem found in UA (fig.~\ref{fig:bec-elev}). These zones were
both protected at rates above the average (fig.~\ref{fig:bec-conch}),
and above the Aichi biodiversity targets. Interior mountain-heather
alpine had large differences in canopy cover and canopy height, while
Boreal Altai Fescue Alpine only showed large differences in height. The
Coastal Mountain-heather Alpine did not any have large forest structural
attribute differences (tbl.~\ref{tbl:vectab}).

@@

Utilizing this information on the proportion of BEC zones protected
(fig.~\ref{fig:bec-conch}), as well as their forest structural
attributes (tbl.~\ref{tbl:vectab}), it is possible to identify which
forest structures need to be added to the PA network in BC. Those BEC
zones with large differences (identified as being \textgreater5\% change
from PA to UA) suggest additional protection is needed to encapsulate
these underrepresented forest structures. For example: the forests in
the Bunchgrass zone have large differences in both canopy cover and
canopy height, with the PA having larger values in both attributes
(tbl:vectab). New PA in this BEC zone should contain forests with
shorter and more open forests. A future avenue of research could be to
incorporate forest structural attributes into spatially optimized PA
placement approaches (Christensen et al. 2009).
